WordRec Experiment

### 2019-01-29 Analysis/process.Rmd
second draft cogsci

```{r}
library(readr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(langcog)
library(ggthemes)
library(lme4)
library(purrr)
theme_set(theme_few())
```

@@

d_sim_transform <-  d_sim_summary %>%
  mutate(normalized =ifelse(condition=='sound_real', mean/0.926, mean)) %>% #Here I only normalize sounds, objects are already normalized
  filter(distance != "iden") %>%
  mutate(mydist = ifelse(distance=="0.6", 1, myscale))%>% # Here I create a ligne for different which were not explicitly asked from participants because it was used as a prototype, thus dist=1
  mutate(labels = ifelse(distance=='0.1','similar', 
                         ifelse(distance=='0.3','intermediate', 
                                ifelse(distance=='sim','similar',
                                       ifelse(distance=='med','intermediate', 'different')))))

#d_sim_summary$distance <- factor(sum_child$concept_dist, levels = c("similar", "different"))
#sum_child$sound_dist <- factor(sum_child$sound_dist, levels = c("similar", "different"))

ggplot(d_sim_transform, 
      aes(x = labels, y = mydist, col=condition)) +
  geom_point()+
  #geom_pointrange(aes(ymin = lower, ymax = upper), 
     #            position = position_dodge(width = .1)) + 
  xlab("Distance") +ylab("rating")+
  theme_few()+
theme(legend.title = element_text(size=11),
      legend.text=element_text(size=11),
      axis.text = element_text(size = 11)
      ) +
  ylim(c(0,1.1))

@@

@@

@@

model2_val <- add_rownames(as.data.frame(confint2(fit_children_2)), "param") %>%
  mutate(val= ifelse(param=='Vr_s',Vr_s_ch, Vr_o_ch),
         model=2, 
         group = "children") %>%
  bind_rows(add_rownames(as.data.frame(confint2(fit_adults_2)), "param") %>%
              mutate(val= ifelse(param=='Vr_s',Vr_s_ad, Vr_o_ad),
                     model=2, 
                     group = "adults"))

@@

>>>>

```{r}
library(readr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(langcog)
library(ggthemes)
library(lme4)
library(nlstools)
library(MuMIn)
library(purrr)
theme_set(theme_few())
```

@@

d_sim_process <- d_sim_summary %>%
  bind_rows(data.frame(condition="obj_real", distance="1", mean= 1, lower=1,upper=1)) %>%
  mutate(stimuli = ifelse(condition =='obj_real','objects','sounds')) %>%
  filter(distance != "iden",
         distance != "0.6") %>%
  mutate(labels = ifelse(distance=='0.1','similar', 
                         ifelse(distance=='0.3','intermediate', 
                                ifelse(distance=='sim','similar',
                                       ifelse(distance=='med','intermediate', 'different'))))) %>%
  select(-condition, -distance)

d_sim_process$labels <- factor(d_sim_process$labels, levels = c("similar","intermediate","different"))

feather::write_feather(d_sim_process, "../saved_data/d_sim_process.feather")

#d_sim_transform <-  d_sim_summary %>%
#  mutate(normalized =ifelse(stimuli=='sounds', mean/0.926, mean))  #Here I only normalize sounds, objects are already normalized

ggplot(d_sim_process, 
      aes(x = labels, y = mean, group = factor(stimuli), col=factor(stimuli))) +
  #geom_point(size=2)+
  geom_line()+
  geom_pointrange(aes(ymin = lower, ymax = upper), 
                 position = position_dodge(width = .1),
                 size=0.2) + 
  scale_colour_discrete(name="Stimuli")+
  theme_few()+
theme(legend.title = element_text(size=11),
      legend.text=element_text(size=11),
      axis.text = element_text(size = 11),
      aspect.ratio = 0.7
      ) +
  ylim(c(0,1.1)) +
  xlab("Stimuli group")+ ylab("Perceptual distance (experimental)")

@@

#Combine both  
data_both_ch <- data_ch %>%
  select(ID, c_dist, s_dist, item_object, item_sound, iscorrect) %>%
  mutate(age = -1)

data_both_ad <- data_ad %>%
  select(ID, c_dist, s_dist, concept, sound,iscorrect) %>%
  rename(item_object = concept,
         item_sound = sound) %>%
  mutate(age = 1)

data_both <- data_both_ch %>%
  bind_rows(data_both_ad)

@@

model_both <- glmer(iscorrect ~ s_dist * c_dist * age+ 
                 (s_dist * c_dist  | ID) + 
                 (c_dist | item_object) + 
                 (s_dist | item_sound) +
                 (s_dist * c_dist | age), 
               data = data_both, family = binomial(),
               glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))

stargazer(model_ch, model_ad, 
          column.labels = c("Children","Adults"),
          model.numbers=FALSE,
          intercept.bottom = FALSE,
          covariate.labels=c("(Intercept)","Sound ","Object","Sound x Object"),
          no.space=TRUE,
          single.row=TRUE,
          star.cutoffs =c(0.05, 0.01, 0.001),
          digits=2,
          omit.stat = "all",
          table.layout ="-c-!t-n",
          header=FALSE,
          #notes=c("[0.*]","[0.**]"),
          title="Estimates of predictor coefficients (and their standard errors) by age group in the regression model")

@@

model2_val <- tibble::rownames_to_column(as.data.frame(confint2(fit_children_2)), "param") %>%
  mutate(val= ifelse(param=='Vr_s',Vr_s_ch, Vr_o_ch),
         model=2, 
         group = "children") %>%
  bind_rows(tibble::rownames_to_column(as.data.frame(confint2(fit_adults_2)), "param") %>%
              mutate(val= ifelse(param=='Vr_s',Vr_s_ad, Vr_o_ad),
                     model=2, 
                     group = "adults"))

#Model comparison

model_comparison <- tibble::rownames_to_column(AIC(fit_adults, fit_adults_2), 'model') %>%
  bind_rows(tibble::rownames_to_column(AIC(fit_children, fit_children_2), 'model'))

@@

feather::write_feather(model_comparison, "../saved_data/model_comparison.feather")
